Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-16 extended_catalog/paper/extended_catalog.tex
done with keiths changes

For each candidate, we generated a map of residual \ts by adding a new
source of spectral index 2 into the region and finding the increase in
likelihood when fitting its flux. \ts maps are useful to look for residual
structure in the sky model.  Figure~\ref{res_tsmaps} shows a residual \ts
map for the extended source IC443.  The residual \ts map indicates that
the spatially extended model for IC443 is a significantly better description
of the observed photons.
We also generated plots of the sum of
all counts within a given distance of the source and compared it to the
model predictions of a point source.  
An example radial integral plot is shown for the extended source IC443
in figure~\ref{four_plots_ic443}(c).  For each source, we also made
Galactic and extragalactic diffuse emission subtracted smoothed counts
maps. Figure~\ref{four_plots_ic443}(d) shows an example for IC443.

% 2FGL J1856.2+0450c = P72Y3047 for
We then inspected the residual \ts, smoothed counts maps, and radial
integral distributions to identify cases in which the extension fit
is clearly biased by large-scale residuals in the diffuse emission
and hence the extension measurement unreliable.  An example of such a
case is shown in figure~\ref{example_bad_fit}. It shows a Galactic and
isotropic diffuse emission subtracted smoothed counts map of this source
using 1-100 \gev photons.  In this region along the Galactic plane,
there appears to be large-scale residual in the diffuse emission. As
a result, 2FGL\,J1856.2+0450c fit to an extension of 1.83\deg and the
result is statistically significant with \tsext=45.4.  By looking at
the residuals, it is clear that this complicated region is not fit well
even though the source's extension is statistically significant. We do
not report sources as extended that fail this inspection.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

For the remaining candidates, 
we took the spatial and spectral model found using \pointlike and
redetermined the spectral 
parameters using
\gtlike.  We used 
the `binned likelihood' mode of \gtlike on a $14\deg\times14\deg$
ROI with a pixel size of 0.03\deg.
We obtained a second measure of \tsext from \gtlike for the extension
and position of the source as determined by \pointlike.
We only considered a source to be significantly extended if $\tsext>16$ with
both \pointlike and \gtlike.

@@

We estimate a systematic error on the extension of a source due to
uncertainty in our knowledge of the angular resolution of the LAT.  Before
launch, the LAT PSF was determined by a detector simulation which was
verified in accelerator tests \citep{atwood_LAT_mission}.  A discrepancy
was found in flight data above a few \gev in the PSF compared to the
shape of bright AGN.  A publication on this issue is in preparation
\citep{lat_on_orbit_psf}.  Subsequently, the PSF was fit empirically to
bright AGN and this empirical parameterization is the default PSF used
in the P7\_V6 IRFs.  To account for this uncertainty in our knowledge of
the PSF, we refit our extended source candidates using the Monte Carlo
representation of the PSF and consider the difference in extension found
using the two PSFs as a systematic error on the extension of a source.
The same approach was used in
\citep{ic443}.  At high energies, we believe that our parameterization
of the PSF from bright AGN is substantially better than the Monte Carlo
representation of the PSF so this systematic errors is conservative.

@@

We estimate a second systematic error on the extension of a source
due to uncertainty in the model of the Galactic diffuse emission by
using an alternative diffuse model. The alternative model was based on
the GALPROP\footnote{GALPROP is a software package for calculating the
Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
in the Galaxy. See \url{http://galprop.stanford.edu/} for details and
references} model used in the LAT analysis of the isotropic diffuse
emission \citep{isotropic_lat}.  
The intensities of various contributions to the galactic
diffuse emission are then fitted individually using a spatial
distribution of the intensities within the ROI 
as predicted by the model.
We distinguish contributions from CR interactions with
the molecular hydrogen, the atomic+ionized hydrogen,
residual gas traced by dust \citep{isabelle_dark_gass},
and the interstellar radiation field. We further
split the contributions from interactions with molecular
and atomic hydrogen to the
Galactic diffuse emission according
to the distance from the Galactic center in
which they are produced. Hence, we replace
the standard diffuse emission model by 18
individually fitted templates to describe individual
components of the diffuse emission.
A similar crosscheck was used in the
LAT Collaboration's analysis of RX J1713.7-3946 \citep{rx_j1713_lat}.

It is not expected that this diffuse model is superior to the standard
LAT model.  But adding degrees of freedom to the background model can
remove likely spurious sources that correlate with features in the
Galactic diffuse emission.  Therefore, this tests systematics that may
be due to incorrect modeling of the diffuse emission in the region.

@@

\section{Analysis of Extended Sources in 2FGL}
\label{validate_known}

@@

Two nearby galaxies the Large Magalenic Cloud and the Small Magalenic
Cloud were included in 2FGL \citep{lmc,smc}.  They were significantly
detected using 1-100 \gev photons. Our
fit extension is comparable to the published result, but we note that
previous publication used a more complicated two Gaussian surface
brightness spatial model when fitting the LMC.

% 3 PWN
Three PWNe Vela X, MSH 15-52, and HESS\,J1825-137 were
included in 2FGL \citep{velax,msh1552,fermi_hess_j1825}.  Using photons
with energy above 10 \gev, we significantly detected the extension of
HESS\,J1825-137.  To improve the model of this source, we removed the
nearby catalog source 2FGL\,J1823.1-1338c which is part of the extended
source.  To avoid confusion with the nearby bright pulsar PSR J1509-5850, MSH 15-52 must be
analyzed at high energies.  Using photons with energies above 10 \gev,
we fit the extension of MSH 15-52 to be consistent with the published
size with an extension significance of \tsext=6.5.

% failed to detect vela x + cen a
Our analysis was unable to resolve Vela X which would have required first
removing the pulsed photons from the Vela pulsar. This is beyond the
scope of this paper.  Our analysis also failed to detect a significant
extension for the Centaurus A Lobes \citep{cen_a_lat}. This is because
the source's emission is significantly different from a uniform
radially symmetric surface brightness.

@@

To validate our method, we test LAT sources associated with AGN for
extension.  \gev emission from AGN is believed to originate from the cores
of kpc-scale jets of distant galaxies.  Therefore AGN are not expected
to be spatially resolvable and provide a good calibration source to
demonstrate the efficacy of our tool.  We note that mpc-scale $\gamma$-ray
halos around AGNs have been hypothesized \citep{pair_halo_paper} which
could be resolved by the LAT However, no such halo has been discovered
in the LAT data so far.

Following 1FGL, the LAT collaboration published a list called 1LAC
of sources that
had a high probability association with AGN \citep{first_agn_cat}.
1FGL had 709 1FGL sources associated with 671 distinct AGN at high
latitude ($|b|>10\deg$).  
Using two years of data and 2FGL, the LAT collaboraiton
associated 1016 2FGL sources
with AGN \citep{second_agn_cat}.
To avoid systematic problems with AGN classification, we
selected 885 out of the 1016 AGN which made it into the clean AGN sub-sample.  An AGN
association is considered clean only if it has a high probability
of association $P\ge 80\%$, if it is the only AGN associated with the
catalog source, and if there are no flags on the source in 2FGL. These
last two conditions are important for our analysis. Source
confusion may look like a spatially extended source and flagged catalog
sources may correlate with unmodeled structure in the diffuse emission.

Of the 885 clean AGN, we select 783 of these 2FGL sources which
are significant above 1 \gev and fit each of them for extension.
A histogram of the \tsext values computed for these AGN is
shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is the
$\chi^2/2$ distribution of equation~\ref{ts_ext_distribution}.
The \tsext distribution for AGN shows good agreement with the
theoretical distribution.  Two sources had $\tsext>10$.  One was due
to incorrectly automatically removing a nearby catalog sources (see
section~\ref{extended_source_search_method}) and the other was due to a
failure of convergence of the point hypothesis.  This result demonstrates
that we can use \tsext as a measure of the statistical significance of
the detection of the extension of a source.

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{source_plots/example_bad_fit.pdf}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
    \caption{
    A Diffuse emission subtracted 1-100 \gev counts map of the region
    around 2FGL\,J1856.2+0450c smoothed by a 0.1\deg Gaussian kernel. The
    red cross and circle are the center and size of the best fit radially
    symmetric source with a uniform intensity profile. The result is
    statistically significant, but the extension encompasses many catalog
    sources and the emission does not look to be uniform. Instead,
    this source is probably fitting large-scale diffuse residual
    features. Although the fit is statistically significant, it likely
    corresponds to residual features of inaccurately modeled diffuse
    emission picked up by the fit.  We manually discard candidates that
    appear like this.
    }
    \label{example_bad_fit}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J0823.3-4248}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
  \caption{A Diffuse emission subtracted 1-100
  \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed
  by a 0.1\deg Gaussian kernel.  The red star is the catalog position
  of this source.  The red cross and circle are the best fit position
  and extension of this source assuming a radially symmetric uniform
  surface brightness.  The two green stars are the positions of the
  sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which were removed
  because they are part of the extended source.  The lower right inset
  is the model predicted emission from a point source with the same
  spectrum as 2FGL\,J0823.4-4305 smoothed by the same Gaussian kernel.
  This source is spatially coincident with the Puppis A SNR. The
  light blue contours correspond to the X-ray image of Puppis A observed by 
  \rosat
  \citep{rosat_puppis_a}. 
  }\label{1FGL_J0823.3-4248}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1628.6-2419c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v2/run.py
  \caption{
  A Diffuse emission subtracted 1-100 \gev counts
  map of (a) the region around 2FGL\,J1627.0-2425 smoothed by a 0.1\deg
  Gaussian kernel (b) also the emission from the background source 
  2FGL\,J1625.7-2526 subtracted.  The red star is the catalog's
  position of this source.  The red cross and circle are the best
  position and extension of this source assuming a radially symmetric
  uniform surface brightness.  The left contours correspond to the
  100 micrometer image observed by IRAS \citep{iras_rho_ophiuci} and the right
  contours correspond to CO emission \citep{co_rho_ophiuci}.
  \todo[inline]{Rewrite CO contours based upon descritipon
  of CO contours in Cygnus Loop paper
  http://arxiv.org/pdf/1108.1833v2
  }
  }\label{1FGL_J1628.6-2419c}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_RX_J1713.7-3946}
    % this plot came from
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
  \end{center}
  \caption{A Diffuse emission subtracted 1-100 \gev
  counts map of (a) the region around 2FGL\,J1712.4-3941 smoothed by
  a 0.25\deg Gaussian kernel and (b) also the emission 
  from the background sources subtracted.
  This source is spatially
  coincident with RX J1713.7-3946 was was recently reported by
  \citep{rx_j1713_lat}.  The light blue contours correspond to the \tev image
  observed by H.E.S.S. \citep{rx_j1713_hess}.  The region was analyzed
  with the same background model as \citep{rx_j1713_lat}.  Source A (blue
  cross) is spatially coincident with 2FGL\,J1715.4-4024c (blue star).
  The gray crosses represent from left to right the position of source B
  and C which were added to the background model. 
  }\label{2FGL_J1712.4-3941}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Vela_Jr}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
  \caption{A Diffuse emission subtracted 10-100
  \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
  by a 0.25\deg Gaussian kernel. The red star is the catalog position of this source.  The red cross
  and circle are the best fit position and extension of the source
  assuming a radially
  symmetric uniform surface brightness.  The inner three green stars
  are (from left to right) 2FGL\,J0853.5-4711, 2FGL\,J0855.4-4625,
  and 2FGL\,J0848.5-4535 which were removed because they are part of
  the extended source.  The farther away green stars are (from left to
  right) 2FGL\,J0901.7-4655 and 2FGL\,J0858.0-4815 which were removed
  because they were not significant above 10 \gev.  The blue cross
  is the relocalized position of 2FGL\,J0854.7-4501.  This extended
  source is spatially coincident with the Vela Jr SNR.  The light
  blue contours correspond to the \tev image of Vela Jr. observed by H.E.S.S
  \citep{vela_jr_hess}.
  }\label{Vela_Jr}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1613.6-5100c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v2/source_1FGL_J1613.6-5100c.pdf
  \caption{
    A Diffuse emission subtracted 10-100
    \gev counts map of the region around 2FGL\,J1615.0-5051 (upper
    left) and 2FGL\,J1615.2-5138 (lower right) smoothed by a 0.1\deg
    Gaussian kernel.  The red stars are the catalog positions of these
    sources.  The red stars and circles are the best fit positions and
    extensions of these sources 
    assuming a radially
    symmetric uniform surface brightness.
    The green star inside the extension of 2FGL\,J1615.2-5138  is
    2FGL\,J1614.9-5212 which was removed because it is part of the
    extended source.  The green stars to the left are 2FGL\,J1619.7-5040c
    and 2FGL\,J1620.6-5111c which were removed because they were
    not significant above 10\gev. These are shown as green stars.
    The light blue
    contours correspond to the \tev image 
    of the extended sources
    HESS\,J1616-508 (left) and the extended source HESS\,J1614-518
    (right)
    observed by H.E.S.S
    \citep{hess_plane_survey}
    2FGL\,J1615.0-5051 is spatially consistent with HESS\,J1616-508 and
    2FGL\,J1615.2-5138 is spatially consistent with HESS\,J1614-518.
  }\label{1FGL_J1613.6-5100c}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1632.9-4802c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
  \caption{A Diffuse emission subtracted 10-100
  \gev counts map of the region around 2FGL\,J1632.4-4753c smoothed by
  a 0.1\deg Gaussian kernel.  This source is in a crowded region.
  The red star is the catalog position of this source.  The red
  cross and circle are the best fit position and extension 2FGL\,J1632.4-4753c 
  assuming a radially
  symmetric uniform surface brightness.
  The three
  green crosses inside the extension are 2FGL
  J1631.7-4720c, 2FGL\,J1630.2-4752, and 2FGL\,J1634.4-4743c.4-4820c
  which were removed because they are part
  of the extended source.  The blue stars and crosses are the catalog
  positions and the relocalized positions of (from left to right)
  2FGL\,J1635.4-4717c and 2FGL\,J1636.3-4740c.  The farther away green
  stars are other catalog sources which were removed because they are
  not significant above 10 \gev.  This extended source is spatially
  coincident with the extended H.E.S.S source HESS\,J1632-478.
  The light blue contours correspond to the \tev image observed by H.E.S.S.
  \citep{hess_plane_survey}.
  }\label{1FGL_J1632.9-4802c}
\end{figure}

>>>>

For each candidate, we generated a map of residual \ts by adding a new
source of spectral index 2 into the region and finding the increase in
likelihood when fitting its flux. \ts maps are useful to look for residual
structure in the sky model.  Figure~\ref{res_tsmaps} shows a residual \ts
map for the extended source IC443.  The residual \ts map indicates that
the spatially extended model for IC443 is a significantly better description
of the observed photons.
We also generated plots of the sum of
all counts within a given distance of the source and compared it to the
model predictions of a point source.  
An example radial integral plot is shown for the extended source IC443
in figure~\ref{four_plots_ic443}(c).  For each source, we also made
diffuse-emission-subtracted smoothed counts
maps. Figure~\ref{four_plots_ic443}(d) shows an example for IC443.

% 2FGL J1856.2+0450c = P72Y3047 for
We then inspected the residual \ts, smoothed counts maps, and radial
integral distributions to identify cases in which the extension fit
is clearly influenced by large-scale residuals in the diffuse emission
and hence the extension measurement unreliable.  An example of such a
case is shown in figure~\ref{example_bad_fit}. It shows a Galactic and
isotropic diffuse-emission-subtracted smoothed counts map of this source
using 1-100 \gev photons.  In this region along the Galactic plane,
there appears to be large-scale residual in the diffuse emission. As
a result, 2FGL\,J1856.2+0450c fit to an extension of 1.83\deg and the
result is statistically significant with \tsext=45.4. However, by looking at
the residuals it is clear that this complicated region is not fit well
even though the source's extension is statistically significant. We do
not report sources as extended that fail this inspection.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

For the remaining candidates, 
we took the spatial and spectral model found using \pointlike and
re-determined the spectral 
parameters using
\gtlike.  We used 
the `binned likelihood' mode of \gtlike on a $14\deg\times14\deg$
ROI with a pixel size of 0.03\deg.
We obtained a second measure of \tsext from \gtlike for the extension
and position of the source as determined by \pointlike.
We only considered a source to be significantly extended if $\tsext>16$ with
both \pointlike and \gtlike.

@@

We estimate a systematic error on the extension of a source due to
uncertainty in our knowledge of the LAT PSF.  Before
launch, the LAT PSF was determined by a detector simulation which was
verified in accelerator tests \citep{atwood_LAT_mission}. However,
in-flight data revealed a discrepancy
above a few \gev in the PSF compared to the
photon angular distribution of bright AGN.  A publication on this issue is in preparation
\citep{lat_on_orbit_psf}.  Subsequently, the PSF was fit empirically to
bright AGN and this empirical parameterization is the default PSF used
in the P7\_V6 IRFs.  To account for this uncertainty in our knowledge of
the PSF, we refit our extended source candidates using the Monte Carlo
representation of the PSF and consider the difference in extension found
using the two PSFs as a systematic error on the extension of a source.
The same approach was used in
\citep{ic443}.  At high energies, we believe that our parameterization
of the PSF from bright AGN is substantially better than the Monte Carlo
representation of the PSF so this estimate of systematic errors is conservative.

@@

We estimate a second systematic error on the extension of a source
due to uncertainty in the model of the Galactic diffuse emission by
using an alternative diffuse model. An alternative model was based upon
GALPROP\footnote{GALPROP is a software package for calculating the
Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
in the Galaxy. See \url{http://galprop.stanford.edu/} for details and
references} and used in the LAT analysis of the isotropic diffuse
emission \citep{isotropic_lat}.  
The intensities of various components to the galactic
diffuse emission are then fitted individually using a spatial
distribution of the intensities within the ROI 
as predicted by the model.
We distinguish contributions from CR interactions with
the molecular hydrogen, the atomic+ionized hydrogen,
residual gas traced by dust \citep{isabelle_dark_gass},
and the interstellar radiation field. We further
split the contributions from interactions with molecular
and atomic hydrogen to the
Galactic diffuse emission according
to the distance from the Galactic center in
which they are produced. Hence, we replace
the standard diffuse emission model by 18
individually fitted templates to describe individual
components of the diffuse emission.
A similar crosscheck was used in the
LAT Collaboration's analysis of RX J1713.7-3946 \citep{rx_j1713_lat}.

It is not expected that this diffuse model is superior to the standard
LAT model that was obtained through an all-sky fit.  But adding degrees of freedom to the background model can
remove likely spurious sources that correlate with features in the
Galactic diffuse emission.  Therefore, this tests systematics that may
be due to incorrect modeling of the diffuse emission in the region.

@@

\section{Analysis of Extended Sources Identified in 2FGL}
\label{validate_known}

@@

Two nearby satellite galaxies of the Milky Way the Large Magalenic Cloud (LMC)
and the Small Magalenic
Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  They were significantly
detected using 1-100 \gev photons. Our
fit extension is comparable to the published result, but we note that
previous LAT collaboration publication on LMC used a more complicated two Gaussian surface
brightness spatial model when fitting it (\citep{lmc}).

% 3 PWN
Three PWNe Vela X, MSH 15-52, and HESS\,J1825-137 were
already identified in 2FGL \citep{velax,msh1552,fermi_hess_j1825}.  
HESS\,J1825-137 was significantly detected using 10-100 \gev photons.
To improve the model of this source, we removed the
nearby catalog source 2FGL\,J1823.1-1338c which is part of the extended
source.  To avoid confusion with the nearby bright pulsar PSR J1509-5850, MSH 15-52 must be
analyzed at high energies.  Using photons with energies above 10 \gev,
we fit the extension of MSH 15-52 to be consistent with the published
size with an extension significance of \tsext=6.5.

% failed to detect vela x + cen a
Our analysis was unable to resolve Vela X which would have required first
removing the pulsed photons from the Vela pulsar which is beyond the
scope of this paper.  Our analysis also failed to detect a significant
extension for the Centaurus A Lobes \citep{cen_a_lat}. This is because
the source's emission is significantly different from a uniform
radially symmetric surface brightness.

@@

To validate our method, we test LAT sources associated with AGN for
extension.  \gev emission from AGN is believed to originate from the cores
of kpc-scale jets of distant galaxies.  Therefore AGN are not expected
to be spatially resolvable by the LAT and provide a good calibration source to
demonstrate the efficacy of our tool.  We note that mpc-scale $\gamma$-ray
halos around AGNs have been hypothesized \citep{pair_halo_paper} which
could be resolved by the LAT However, no such halo has been discovered
in the LAT data so far.

Following 1FGL, the LAT collaboration published a list 
of sources that
had a high probability association with AGN 
called 1LAC \citep{first_agn_cat}.
1FGL had 709 1FGL sources associated with 671 distinct AGN at high
latitude ($|b|>10\deg$).  
Using two years of data and 2FGL, the LAT collaboration
associated 1016 2FGL sources
with AGN called 2LAC \citep{second_agn_cat}.
To avoid systematic problems with AGN classification, we
selected 885 out of the 1016 AGN which made it into the clean AGN sub-sample.  An AGN
association is considered clean only if it has a high probability
of association $P\ge 80\%$, if it is the only AGN associated with the
catalog source, and if there are no flags on the source in 2FGL. These
last two conditions are important for our analysis. Source
confusion may look like a spatially extended source and flagged catalog
sources may correlate with unmodeled structure in the diffuse emission.

Of the 885 clean AGN, we select 783 of these 2FGL sources which
are significantly-detected above 1 \gev and fit each of them for extension.
A histogram of the \tsext values computed for these AGN is
shown in figure~\ref{agn_ts_ext}. Overlaid on the plot is the
$\chi^2/2$ distribution of equation~\ref{ts_ext_distribution}.
The \tsext distribution for AGN shows good agreement with the
theoretical distribution.  Two sources had $\tsext>10$.  One was due
to incorrectly automatically removing a nearby catalog sources (see
section~\ref{extended_source_search_method}) and the other was due to a
failure of convergence of the point hypothesis.  This result demonstrates
that we can use \tsext as a measure of the statistical significance of
the detection of the extension of a source.

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics{source_plots/example_bad_fit.pdf}
    % taken from /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/example_bad_fit/v3/run.py
    \caption{
    A diffuse-emission-subtracted 1-100 \gev counts map of the region
    around 2FGL\,J1856.2+0450c smoothed by a 0.1\deg Gaussian kernel. The
    red cross and circle are the center and size of the best fit radially
    symmetric source with a uniform intensity profile. The result is
    statistically significant, but the extension encompasses many catalog
    sources and the emission does not look to be uniform. Instead,
    this source is probably fitting large-scale diffuse residual
    features. Although the fit is statistically significant, it likely
    corresponds to residual features of inaccurately modeled diffuse
    emission picked up by the fit.  We manually discard candidates that
    appear like this.
    }
    \label{example_bad_fit}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J0823.3-4248}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J0823.3-4248/v2/source_1FGL_J0823.3-4248.pdf
  \caption{A diffuse-emission-subtracted 1-100
  \gev counts map of the region around 2FGL\,J0823.0-4246 smoothed
  by a 0.1\deg Gaussian kernel.  The red star is the catalog position
  of this source.  The red cross and circle are the best fit position
  and extension of this source assuming a radially symmetric uniform
  surface brightness.  The two green stars are the positions of the
  sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which were removed
  because they are part of the extended source.  The lower right inset
  is the model predicted emission from a point source with the same
  spectrum as 2FGL\,J0823.4-4305 smoothed by the same Gaussian kernel.
  This source is spatially coincident with the Puppis A SNR. The
  light blue contours correspond to the X-ray image of Puppis A observed by 
  \rosat
  \citep{rosat_puppis_a}. 
  }\label{1FGL_J0823.3-4248}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1628.6-2419c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1628.6-2419c/v2/run.py
  \caption{
  A diffuse-emission-subtracted 1-100 \gev counts
  map of (a) the region around 2FGL\,J1627.0-2425 smoothed by a 0.1\deg
  Gaussian kernel (b) also the emission from the background source 
  2FGL\,J1625.7-2526 subtracted.  The red star is the catalog's
  position of this source.  The red cross and circle are the best
  position and extension of this source assuming a radially symmetric
  uniform surface brightness.  The left contours correspond to the
  100 micrometer image observed by IRAS \citep{iras_rho_ophiuci} and the right
  contours correspond to CO emission \citep{co_rho_ophiuci}.
  \todo[inline]{Rewrite CO contours based upon descritipon
  of CO contours in Cygnus Loop paper
  http://arxiv.org/pdf/1108.1833v2
  }
  }\label{1FGL_J1628.6-2419c}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_RX_J1713.7-3946}
    % this plot came from
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/RX_J1713.7-3946/v6/run.py
  \end{center}
  \caption{A diffuse-emission-subtracted 1-100 \gev
  counts map of (a) the region around 2FGL\,J1712.4-3941 smoothed by
  a 0.25\deg Gaussian kernel and (b) also the emission 
  from the background sources subtracted.
  This source is spatially
  coincident with RX J1713.7-3946 was was recently reported by
  \citep{rx_j1713_lat}.  The light blue contours correspond to the \tev image
  observed by H.E.S.S. \citep{rx_j1713_hess}.  The region was analyzed
  with the same background model as \citep{rx_j1713_lat}.  Source A (blue
  cross) is spatially coincident with 2FGL\,J1715.4-4024c (blue star).
  The gray crosses represent from left to right the position of source B
  and C which were added to the background model. 
  }\label{2FGL_J1712.4-3941}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_Vela_Jr}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/Vela_Jr/v2/source_Vela_Jr.pdf
  \caption{A diffuse-emission-subtracted 10-100
  \gev counts map of the region around 2FGL\,J0851.7-4635 smoothed
  by a 0.25\deg Gaussian kernel. The red star is the catalog position of this source.  The red cross
  and circle are the best fit position and extension of the source
  assuming a radially
  symmetric uniform surface brightness.  The inner three green stars
  are (from left to right) 2FGL\,J0853.5-4711, 2FGL\,J0855.4-4625,
  and 2FGL\,J0848.5-4535 which were removed because they are part of
  the extended source.  The farther away green stars are (from left to
  right) 2FGL\,J0901.7-4655 and 2FGL\,J0858.0-4815 which were removed
  because they were not significant above 10 \gev.  The blue cross
  is the relocalized position of 2FGL\,J0854.7-4501.  This extended
  source is spatially coincident with the Vela Jr SNR.  The light
  blue contours correspond to the \tev image of Vela Jr. observed by H.E.S.S
  \citep{vela_jr_hess}.
  }\label{Vela_Jr}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1613.6-5100c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1613.6-5100c/v2/source_1FGL_J1613.6-5100c.pdf
  \caption{
    A diffuse-emission-subtracted 10-100
    \gev counts map of the region around 2FGL\,J1615.0-5051 (upper
    left) and 2FGL\,J1615.2-5138 (lower right) smoothed by a 0.1\deg
    Gaussian kernel.  The red stars are the catalog positions of these
    sources.  The red stars and circles are the best fit positions and
    extensions of these sources 
    assuming a radially
    symmetric uniform surface brightness.
    The green star inside the extension of 2FGL\,J1615.2-5138  is
    2FGL\,J1614.9-5212 which was removed because it is part of the
    extended source.  The green stars to the left are 2FGL\,J1619.7-5040c
    and 2FGL\,J1620.6-5111c which were removed because they were
    not significant above 10\gev. These are shown as green stars.
    The light blue
    contours correspond to the \tev image 
    of the extended sources
    HESS\,J1616-508 (left) and the extended source HESS\,J1614-518
    (right)
    observed by H.E.S.S
    \citep{hess_plane_survey}
    2FGL\,J1615.0-5051 is spatially consistent with HESS\,J1616-508 and
    2FGL\,J1615.2-5138 is spatially consistent with HESS\,J1614-518.
  }\label{1FGL_J1613.6-5100c}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1632.9-4802c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1632.9-4802c/v2/source_1FGL_J1632.9-4802c.pdf
  \caption{A diffuse-emission-subtracted 10-100
  \gev counts map of the region around 2FGL\,J1632.4-4753c smoothed by
  a 0.1\deg Gaussian kernel.  This source is in a crowded region.
  The red star is the catalog position of this source.  The red
  cross and circle are the best fit position and extension 2FGL\,J1632.4-4753c 
  assuming a radially
  symmetric uniform surface brightness.
  The three
  green crosses inside the extension are 2FGL
  J1631.7-4720c, 2FGL\,J1630.2-4752, and 2FGL\,J1634.4-4743c.4-4820c
  which were removed because they are part
  of the extended source.  The blue stars and crosses are the catalog
  positions and the relocalized positions of (from left to right)
  2FGL\,J1635.4-4717c and 2FGL\,J1636.3-4740c.  The farther away green
  stars are other catalog sources which were removed because they are
  not significant above 10 \gev.  This extended source is spatially
  coincident with the extended H.E.S.S source HESS\,J1632-478.
  The light blue contours correspond to the \tev image observed by H.E.S.S.
  \citep{hess_plane_survey}.
  }\label{1FGL_J1632.9-4802c}
\end{figure}

\begin{figure}
  \begin{center}
    \includegraphics[type=pdf,ext=.pdf,read=.pdf]{source_plots/source_1FGL_J1837.5-0659c}
  \end{center}
  % this plot came from 
  % /u/gl/lande/work/fermi/extended_catalog/2FGL/plots_for_paper/source_plots/1FGL_J1837.5-0659c/v2/source_1FGL_J1837.5-0659c.pdf
  \caption{
  A diffuse-emission-subtracted 10-100 \gev counts map of
  (a)
  the region around 2FGL\,J1837.3-0700c smoothed by a 0.1\deg Gaussian
  kernel and (b) also the emission from the background 
  sources subtracted.  The red
  star is the catalog position of this source. The red cross and circle
  are the best fit position and extension  of 2FGL\,J1837.3-0700c 
  assuming a radially
  symmetric uniform surface brightness. The blue stars and crosses are the
  catalog position and the relocalized position of (from left to right)
  2FGL\,J1839.3-0558c, 2FGL\,J1836.8-0623c, and 2FGL\,J1834.7-0705c.
  The green cross inside the extension is 2FGL\,J1835.5-0649 which
  was removed because it is part of the extended source.  The farther
  away green star is 2FGL J1839.0-0539 which was removed because
  it is not significant above 10 \gev.  This source is spatially
  coincident with the \tev source HESS\,J1837-069.  The light blue
  contours correspond to the \tev image observed by H.E.S.S.
  \citep{hess_plane_survey}.}\label{1FGL_J1837.5-0659c}
\end{figure}
